Working Title - CUT Research Paper

### 2019-04-15 CUT/paper.tex
references for open book literature survey

On the positive side for Open Book exams, it has been shown that they lead to significantly lower test anxiety and stress among students leading up to the exam TODOCITE(Broyles, Cyr, and Korsen). This reduction in tension is hypothesized to lead to better study habits, such as focusing on understanding over rote memorization. It was found by (TODOCITE Weber, McBee and Krebs) that there are slight gains in student performance on Open Book exams over Closed Book exams. They also corroborate the findings of (Broyles, Cyr, and Korsen) that student test anxiety is reduced in an Open Book exam setting. 

@@

A study of the empirical literature on Open Book exams conducted by TODOCITE (Theophilides and Dionysiou) supports the assertions that Open Book exams lead to lower test anxiety, and less focus on memorization over understanding. But their study also shows that Open Book examinations do not lead to higher test scores, in particular where critical-thinking questions are concerned. The findings of TODOCITE (Agarwal et al.) are even more lukewarm. They find that the effect of testing on student retention is equal between Open Book and Closed Book exams. Separate studies by TODOCITE (Ioannidou) and (Boniface) found that student reliance on their permitted notes during an Open Book exam correlated with lower test scores. The findings of Ioannidou further indicate that critical-thinking questions are not effected with any statistical significance by the variable of whether an exam is Open or Closed Book. Moore and Jensen) TODOCITE found that Open Book exams diminish long term retention of material among Biology students, and promote shallow-learning study strategies. The results of TODOCITE (Heijne-Penninga) support these findings, indicating that Closed Book exams do a better job of promoting deep-learning strategies among students than Open Book Exams.

>>>>

On the positive side for Open Book exams, it has been shown that they lead to significantly lower test anxiety and stress among students leading up to the exam~\cite{broyles2005open}. This reduction in tension is hypothesized to lead to better study habits, such as focusing on understanding over rote memorization. It was found by~\cite{broyles2005open} that there are slight gains in student performance on Open Book exams over Closed Book exams. They also corroborate the findings of~\cite{broyles2005open} that student test anxiety is reduced in an Open Book exam setting. 

@@

A study of the empirical literature on Open Book exams conducted by~\cite{theophilides2000study} supports the assertions that Open Book exams lead to lower test anxiety, and less focus on memorization over understanding. But their study also shows that Open Book examinations do not lead to higher test scores, in particular where critical-thinking questions are concerned. The findings of~\cite{agarwal2008examining} are even more lukewarm. They find that the effect of testing on student retention is equal between Open Book and Closed Book exams. Separate studies by~\cite{ioannidou1997testing} and~\cite{boniface1985candidates} found that student reliance on their permitted notes during an Open Book exam correlated with lower test scores. The findings of Ioannidou further indicate that critical-thinking questions are not effected with any statistical significance by the variable of whether an exam is Open or Closed Book. \cite{moore2007open} found that Open Book exams diminish long term retention of material among Biology students, and promote shallow-learning study strategies. The results of~\cite{heijne2011directing} support these findings, indicating that Closed Book exams do a better job of promoting deep-learning strategies among students than Open Book Exams.
